---
title: "HW3"
author: "Chris Richardson"
date: "2022-11-11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The below chunk of code allow me to handle an error with the parathyroidSE package. When attempting to install it, I was notifed with:
  Warning in install.packages :
    package ‘parathyroidSE’ is not available for this version of R
  
  A version of this package for your version of R might be available elsewhere,
  see the ideas at
  https://cran.r-project.org/doc/manuals/r-patched/R-admin.html#Installing-packages

I found the suggest solution at: https://bioconductor.org/packages/release/data/experiment/html/parathyroidSE.html
This same solution was applied to all packages that did not install ininitally. 

```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("parathyroidSE")
```
```{r}
BiocManager::install("DESeq2")
```

```{r}
BiocManager::install("airway")
```

```{r}
BiocManager::install("apeglm")
```

```{r}
BiocManager::install("EnhancedVolcano")
```

```{r}
BiocManager::install("AnnotationDbi")
```

```{r}
BiocManager::install("org.Hs.eg.db")a
```

```{r}
BiocManager::install("goseq")
```

```{r}
require(parathyroidSE)
data(parathyroidGenesSE)
parathyroidGenesSE
```


```{r }
require(DESeq2)
require(airway)
require(pheatmap)
require(ggplot2)
require(apeglm)
require(EnhancedVolcano)
require(AnnotationDbi)
require(org.Hs.eg.db)
require(goseq)
require(tidyverse)
require(gplots)
require(data.table)
```

```{r}
require(parathyroidSE)
data(parathyroidGenesSE)
patterns <- c("0$", "3$", "5$", "7$")
se <- parathyroidGenesSE
data(airway)
te <- airway
sedf <- as.data.frame(colData(se))
sedf
patterns
```

se2 <- parathyroidGenesSE[(parathyroidGenesSE$sample %in%"SRS[0-9][0-9][0-9][0-9][0-9]5","SRS[0-9][0-9][0-9][0-9][0-9]3","SRS[0-9][0-9][0-9][0-9][0-9]0","SRS[0-9][0-9][0-9][0-9][0-9]7

, sedf$sample ==  "3$" , sedf$sample ==  "5$" , sedf$sample ==  "7$"

```{r}
library(dplyr)
sedf$sample
sedf2  <- sedf %>% filter(sample ==  "6$")
#sedf2 <- sedf[sedf$sample %in% c("0$"),]
sedf2
dds <- DESeqDataSet(se,design = ~ patient + treatment + time)
dds
design(dds)
```
```{r}
se
```

